Combined Task and Motion Planner through an Interface Layer

### 2015-04-18 documentation/draft.tex
filled in table

@@

The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.  Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.  In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the plan more complicated.  In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.  An analysis of the benefits of this approach are outlined in the benchmarking section.

@@

\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|}
\hline
Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
Horizontal Line & 3 & ? & ? & ? & ?\\
& 5 & ? & ? & ? & ?\\
& 7 & ? & ? & ? & ?\\
& 9 & ? & ? & ? & ?\\
& 11 & ? & ? & ? & ?\\
& 13 & ? & ? & ? & ?\\
\hline
Vertical lLne & 3 & ? & ? & ? & ?\\
& 5 & ? & ? & ? & ?\\
& 7 & ? & ? & ? & ?\\
& 9 & ? & ? & ? & ?\\
& 11 & ? & ? & ? & ?\\
& 13 & ? & ? & ? & ?\\ 
\hline
X & 5 & ? & ? & ? & ?\\
& 9 & ? & ? & ? & ?\\
& 13 & ? & ? & ? & ?\\
& 17 & ? & ? & ? & ?\\
& 21 & ? & ? & ? & ?\\
& 25 & ? & ? & ? & ?\\ 
\hline
Cross & 5 & ? & ? & ? & ?\\
& 9 & ? & ? & ? & ?\\
& 13 & ? & ? & ? & ?\\
& 17 & ? & ? & ? & ?\\
& 21 & ? & ? & ? & ?\\
& 25 & ? & ? & ? & ?\\ 
\hline
Square & 9 & ? & ? & ? & ?\\
& 25 & ? & ? & ? & ?\\
& 49 & ? & ? & ? & ?\\
& 81 & ? & ? & ? & ?\\
& 121 & ? & ? & ? & ?\\
& 169 & ? & ? & ? & ?\\ 
\hline

>>>>

\subsubsection{Algorithm Improvements}

The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.  Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.  In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the high level plan more complicated.  In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.  An analysis of the benefits of this approach are outlined in the benchmarking section.

@@

The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.  For our version of the algorithm, every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.

@@

\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|}
\hline
Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
Horizontal Line & 3 & 12 & 3 & 1 & .023\\
& 5 & 24 & 4 & 1 & .028\\
& 7 & 36 & 4 & 1 & .029\\
& 9 & 48 & 4 & 1 & .029\\
& 11 & 60 & 4 & 1 & .034\\
& 13 & 72 & 4 & 1 & .037\\
\hline
Vertical Line & 3 & 12 & 4 & 1 & .024\\
& 5 & 24 & 4 & 1 & .027\\
& 7 & 36 & 4 & 1 & .028\\
& 9 & 48 & 4 & 1 & .028\\
& 11 & 60 & 4 & 1 & .037\\
& 13 & 72 & 4 & 1 & .036\\ 
\hline
X & 5 & 8 & 2 & 1 & .026\\
& 9 & 16 & 2 & 1 & .034\\
& 13 & 24 & 2 & 1 & .036\\
& 17 & 32 & 2 & 1 & .047\\
& 21 & 40 & 2 & 1 & .066\\
& 25 & 48 & 2 & 1 & .079\\ 
\hline
Cross & 5 & 20 & 39 & 3 & .16\\
& 9 & 44 & 50 & 2 & .20\\
& 13 & 68 & 59 & 2 & .23\\
& 17 & 92 & 71 & 3 & .26\\
& 21 & 116 & 78 & 3 & .31\\
& 25 & 140 & 77 & 3 & .39\\ 
\hline
Square & 9 & 56 & 54 & 2 & .16\\
& 25 & 176 & 294 & 6 & 1.06\\
& 49 & 360 & 818 & 10 & 5.07\\
& 81 & 608 & 3177 & 24 & 34.68\\
& 121 & 920 & 3681 & 22 & 87.06\\
& 169 & 1296 & 14216 & 57 & 518.61\\ 
\hline
